---
title: "Project 3: STATProject3 Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{STATProject3 Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(STATProject3)
library(ggplot2)
```

## Introduction

This package can be installed using either of the following:
```{r eval=FALSE}
library(STAT302package)
devtools::install_github("thestrangelybrown/STAT302package", build_vignette = TRUE, build_opts = c())
```
The package contains 4 functions: `my_t_test`, `my_lm`, `my_knn_cv`, `my_rf_cv` which are inferential and/or predictive statistical methods. Their applications vary and examples on how to use them are demonstrated below.

## Part 1: Using my_t_test

```{r}
# Test if mean is not equal to 60
my_gapminder <- gapminder
my_t_test(my_gapminder$lifeExp, "two.sided", 60)
```

Using a p-value cutoff of 0.05, we cannot reject the null hypothesis (mu = 60) as our t-test has a p-value of 0.09.

```{r}
# Test if mean is less than 60
my_t_test(my_gapminder$lifeExp, "less", 60)
```

Using a p-value cutoff of 0.05, we can reject the null hypothesis (mu = 60) as our t-test has a p-value of 0.0466, so mu < 60.

```{r}
# Test if mean is greater than 60
my_t_test(my_gapminder$lifeExp, "greater", 60)
```

Using a p-value cutoff of 0.05, we cannot reject the null hypothesis (mu = 60) as our t-test has a p-value of 0.95.

## Part 2: Using my_lm

```{r warning=FALSE}
pred_lifeExp <- my_lm(formula = my_gapminder$lifeExp ~ my_gapminder$gdpPercap + my_gapminder$continent, data = my_gapminder)
print(pred_lifeExp)
```

The gdpPercap coefficient `r pred_lifeExp[2,1]` represents how much each change in gdpPercap affects the predicted change in lifeExp. We accept this value as accurate because its associated p-value is `r pred_lifeExp[2,4]` which is less than 0.05.

```{r}
# FINDING fitted yhat
# getting the matrix of the estimates value 
my_estimates <- as.matrix(pred_lifeExp[,"estimate"])

# fitting data into matrix to create x matrix
x_mat <- model.matrix(lifeExp ~ gdpPercap + continent, my_gapminder)

# matrix multiplication to get yhat 
predicted <- x_mat %*% my_estimates
my_df <- data.frame(actual = my_gapminder$lifeExp, predicted = predicted)

# plot predicted vs actual
ggplot(my_df, aes(x = actual, y = predicted)) + 
  geom_point() +
  labs(title = "Actual vs Predicted", 
       x = "Actual Values", 
       y = "Predicted Values") +
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 14))
```

Each predicted value varies in its relation to the actual values with the points forming noticeable horizontal lines on the plot. Hence our predicted model is not very good.

## Part 3: Using my_knn_cv

```{r}
penguins <- tidyr::drop_na(my_penguins)
data1 <- penguins[c("bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g")]
cl1 <- penguins["species"]
final <- matrix(0, ncol = 2, nrow = 10)


for (i in 1:10) {
  result = my_knn_cv(data1, cl1, i, 5)
  final[i,1] = result$cv_err[1,2]
}

print(final)
```

## Part 4: Using my_rf_cv

```{r}

```
